### 2022-04-14 paper2.tex
copyedits, add desc stat table

\hypertarget{paper-2}{%
\chapter{information seeking Behaviors for Information on COVID-19 Vaccinations}\label{paper-2}}

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

@@

\hypertarget{intro-1}{%
\section{Introduction}\label{intro-1}}

@@

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
\citep{starbird19, kata10}. While no belief in false information can be thought
of as harmless \citep{douglas21} some discredited theories such as 'vaccines
cause autism' have major ramifications for both the individual and public
health. For example, a newfound public resistance to vaccination against Measles
by so-called 'anti-vaxxers' caused a 17\% increase in rates worldwide in 2019.
This increase killed  142,000 people, most of whom were children under the age
of five \citep{givetash19}. However, even in the ever-evolving research agenda
of misinformation and infodemiology \citep{eysenbach02}, much of the research
focuses on the 'push' or 'supply' side of information, like spaces where
individuals first encounter with conspiracy theories or other information
\citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.

The lack of research in which modalities are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and well-being
of individuals in our society. Even outside of the misinformation literature,
much of the research conducted in social networks and communication focus on
senders, influencers, and persuasion strategies
\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955,
lazarsfeldPeopleChoice1944}, rather than on “the receiver as an active
information seeker and processor."
\citep{johnsonComprehensiveModelCancerRelated1993} \citep[for an exception,
see]{eysenbach09}.

I use the case of information around COVID-19 vaccinations to explore the
variation of usage of information search modalities. In doing so, I seek to
answer how computer-mediated or interpersonal information seeking strategies
vary across populations in their search for information about COVID-19
vaccinations and investigate how these strategies affect vaccination uptake.
Specifically, this article answers two research questions: (1) How do
computer-mediated or interpersonal information seeking strategies vary across
populations? (2) How does the information search modality utilized affect
COVID-19 Vaccination uptake?

Before addressing the results to these research questions, I offer an overview
of the current state of social science literature in regards to information
seeking strategies and providing a description of the research methodology and
analytic sample. I then discuss the implications of these findings for the
sociological understanding of information search and vaccination uptake.

@@

One way to find information is to activate network ties to secure information
through a form of social support. Social support, while previously used
interchangeably with the terms social networks and social integration
\citep{houseStructuresProcessesSocial1988}, are the emotional, informational,
and instrumental assistance functions performed between social ties and have
strong and measurable association with health outcomes
\citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
Informational support is the process of seeking “help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support” \citep[][p. 640]{winemiller_etal93}.
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that “facilitates
coping with life stresses… that may be exchanged among members of a support
network” \citet[][p. 260]{brashersInformationSeekingAvoiding2002}.These
definitions help to differentiate between seeking information through social
ties or through something anonymous like online search; a need for coping or
deeper understanding of important matters is thought to sway that decision.

Social support has long been theorized to stem from core discussion networks and
much of the historical social support surveys only examined these core networks.
The underlying assumption is that individuals reach out to a handful of strong
ties when in need of support, which could be elicited in surveys using name
generators \citep{marsdenCoreDiscussionNetworks1987}. This approach has yielded
important insights, but largely overlooks crucial processes of resource
activation \citep{hurlbertCoreNetworksTie2000, perrySocialNetworkActivation2015,
smithDonPutMy2005}. For instance, Small \citet{smallSomeoneTalk2017} shows that
the core discussion network does not capture how people activate social support
in practice and indicates that people draw on much broader social connections
for support, reminiscent of the weak ties research by Granovetter
\citet{granovetterStrengthWeakTies1973}. There is ongoing research investigating
how weak-tie support holds for different support types based on the architecture
put forward by \citet{houseStructuresProcessesSocial1988} of instrumental,
emotional, and informational support.

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”, or the utilization of internet search engines. As the
online environment began penetrating all facets of modern human life, it makes
sense that performing online search has become one of the most convenient
modalities for information search. Small \citet{smallSomeoneTalk2017} showed
that Graduate students often confided in a "miscellaneous classmates encountered
down the hall" (p. 176) instead of established and trusted confidants because
they simply were there at the right time. I theorize that online search engines
may be the most frictionless and costless mode of support. No social capital or
relationship is necessary when choosing to utilize a search engine.

@@

There are important factors that can influence information seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}. UGT
posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s
\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible
with Lazarsfeld and Katz’s theory of two-step flow
\cite{katzPersonalInfluencePart1955} because people can choose their media and
the opinion leaders they follow. Modern-day theorists have extended UGT theory
and classified the uses and gratifications of the internet and of social media.
\citet{staffordDeterminingUsesGratifications2004} theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties.
\citet{leungGenerationalDifferencesContent2013} theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

@@

\begin{hyp}[H\ref{hyp:drgooglefriend}] \label{hyp:drgooglefriend}
Seeking information from experts, search engines, and other people
will be the most common modes of information search. 
\end{hyp}

@@

The data used for this research project are based on original survey data
collected between December 03, 2021 through December 12, 2021. This survey was
hosted on Qualtrics and participants were paid and recruited using Amazon Turk
(MTurk). Potential MTurkers were invited to participate if they were located in
the United States, had a task rate approval of over 95 percent, had completed 50
tasks, and had not completed this survey in previous sessions. The total valid
survey responses (\emph{n} = 948) were selected from a total of 1,066
respondents; some responses were disqualified due to a few factors such as
detected usage of a VPN, random answer clicking (determined by illogical
responses), poor quality typed responses (e.g., social network alters
consistently named random nouns), or taking the survey more than once. The
sample is slightly gender unbalanced, skewing towards male respondents. For the
respondents who provided their zip code (p = 0.98), the sample is quite balanced
with a slight skew towards MTurkers in the South (p = 0.41).

The survey took an average of 24.48 minutes with a standard deviation of 13.23
minutes. The shortest valid survey took 3.75 minutes and the longest took 111.08
minutes. Participants received \$6.00 in compensation for their participation in
the survey \footnote{All funding for this survey was provided by a Grant from
the Summer Institute in Computational Social Science and the Russell Sage
Foundation.}. The survey consisted of two main parts. The first portion of the
survey is a replication of they survey conducted by
\citet{smallSomeoneTalk2017}. In this section, we expand Small's research on
support activation by segregating weak-tie social support into instrumental,
emotional, and informational categories
\citep[see][]{houseStructuresProcessesSocial1988}. The second part of the survey
focuses on network resource activation and information seeking behaviors of
individuals regarding COVID-19 vaccinations for this paper.

\input{tables/paper2/table-1-ind}

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

\hypertarget{sought-information}{%
\subsubsection{Sought Information}\label{sought-information}}

@@

Further dependent variables segment the above question into multiple options;
``How did you look for information about the COVID-19 vaccine?'' Respondents
were posed with 5 responses and `other,' of which they could select multiple.
The largest proportion, 44\%, asked their `doctor or another health
professional'. About 42\% said they asked, `a person like friend, neighbor, or
family member that [they] know'. An additional 41\% searched `for [their]
question using an online search engine such as Google or Bing'. About a quarter
of the sample, 27\%, `posted queries in an online discussion group, listserv, or
other online forum like a Facebook Group or Subreddit'. And finally, 18\% of the
sample `posted queries on a social networking site such as Facebook timeline,
Twitter status update, or LinkedIn'. Much of the question wording and the
specific categories of search were inspired by ICPSR project 37220
\citep{scanlon19}.

@@

\input{tables/paper2/table-2-dep}

Another Dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received or plans to receive a vaccination
against COVID-19. For this survey, the number of doses or timeline of receipt
were less relevant to the research question. This variable instead focuses on
intent or opinion about the vaccine. About 87\% have a positive view about the
vaccine. This construct is made through the combination of two survey items. The
first item is actual vaccination status, obtained through the question `Did you
receive a COVID-19 vaccine?' 84\% of the sample said that they had indeed
received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}). As the
national vaccination rate is closer to 75\% \citep{cdc20}, this indicates some
bias in our sample that must be acknowledged: either MTurkers are more likely to
be vaccinated that the normal population (sampling bias) or there is some
conformity bias in the responses causing survey takers to provide false answers.
The second survey item that contributes to `Vaccination Outlook' was only given
to those who had not responded `yes' to the to their vaccination status. These
respondents were asked `Do you plan to receive a vaccine for the prevention of
the COVID-19 virus?' Of those who were asked this question (n = 147), 9\% said
they were `definitely yes' getting the vaccine; 9\% said they were `probably
yes' going to receive vaccine. The rest of the sample was more unsure: 15\% said
they `Might or might not,' 26\% said `Probably not,' and finally 41\% said they
would `definitely not' receive the vaccine. The variable `Vaccination Outlook'
indicates that either the respondent received a COVID-19 vaccine or either
probably or definitely will in the future.

\hypertarget{independent-variables}{%
\subsubsection{Independent Variables}\label{independent-variables}}

The first independent variables used in this analysis are based on the question,
`In the past 12 months, without searching for it, did you receive information
about the COVID-19 vaccine from \ldots{} (check all sources you received
information from).' This differs from the `How did you look for information'
question above because this is based on passive reception of information. The
largest proportion of respondents had received information from "a person like
friend, neighbor, or family member that [they] know" (\(\widehat{p}\) = 67\%).
Respondents also commonly received information from a television news channel or
a newspaper, about 65\% of the sample. 47\% of the sample had received
information from their doctor or other health professional, while 40\% received
information from a social networking site such as Facebook timeline, Twitter
status update, or LinkedIn. Finally, the lowest proportion of the sample had
received information from an online discussion group, listserv, or other online
forum like a Facebook group or subreddit (\(\widehat{p}\) = 35\%).

@@

\hypertarget{analysis}{%
\section{Analysis}\label{analysis}}

My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-ind} \&
\ref{tab:table-2-dep}, I present descriptive statistics for all study variables,
including variable ranges, means, and standard deviations. For this paper, I
rely heavily on logistic regression, modeled in \texttt{r}; specifically, I fit
a series of binomial generalized linear models with a logit link
\citep{venables2002a}, otherwise known as logistic regression model
\citep{hothorn2006handbook}. This approach is appropriate because the data are
non-nested, cross-sectional data with binary independent variables. In Table
\ref{tab:table-model-1} \footnote{All Tables in this paper were created with the
modelsummary package in \texttt{r} \citep{modelsummary}},I fit a logistic
regression model predicting whether someone sought information about COVID-19
using their sources of information (`Received info') as well as various
demographic variables such as age, education level and race. Figure
\ref{fig:plot-model-1} then illustrates the relationship between the
coefficients and information seeking.\footnote{Figures in this paper were all
created using the \texttt{r} packages jtools \citep{jtools} and ggplot2
\citep{wickham_etal, wickham11}}. In Table \ref{tab:model-2-phi}, I disaggregate
information seeking behaviors by investigating the difference in proportions of
each of the 5 different avenues of seeking information about COVID-19: from
another person, from a doctor, on an online forum, on a social networking site,
or using an online search tool. I investigate these differences through a phi
coefficient \citep{warrens08}, otherwise known as a mean square contingency
coefficient, which is used to investigate the degree of association between two
binary variables.\footnote{To calculate the Phi Coefficient, I utilize the Psych
\texttt{r} package \citep{psych}} I then investigate the associations between my
predictors and the five information search modalities by modelling a series of
logistic regressions in Table \ref{tab:table-model-2}. Finally, in Table
\ref{tab:table-model-3}, I investigate whether there is a relationship between
information exposure sources, information seeking behaviors and the choice to
get vaccinated against COVID-19 through a logistic regression model predicting
Vaccination Outlook. Figure \ref{fig:plot-model-3} then illustrates the
relationship between the coefficients and vaccination outlook.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{information seeking}{%
\subsection{Information Seeking}\label{information seeking}}

@@

\hypertarget{information-search-modalities}{%
\subsection{Information Search Modalities}\label{information-search-modalities}}

@@

To investigate how each Information Search modality are related to each other
using the Phi Coefficient ($\phi$) of binary association between each
Information Search modality pair. The Phi coefficient can be interpreted like a
correlation coefficient, with numbers closer to -1 indicating a very strong
negative relationship and those closer to positive 1 indicating a very strong
positive relationship (Warrens 2008). Table \ref{tab:model-2-phi} shows the
results of these coefficients. Out of the five information search modalities
investigated, there is evidence that the modalities are distinctly different
concepts because most coefficients fall under 0.3, the general cutoff for
correlation coefficients to indicate a relationship. There does seem to be a
relationship between Online Forums and social networking sites, possibly due to
an individual's latent propensity to use online networks over in-person
networks. These coefficients indicate a weak relationship between any two
modalities of information search and that respondents in my sample utilize each
of these a little bit differently.

I find that indeed the most common modalities are asking a doctor, asking a
friend, and asking a search engine which confirms Hypothesis
\ref{hyp:drgooglefriend}. However, because the modalities 95\% confidence
intervals in Table \ref{tab:table-1-ind} are overlapping, I fail to find
evidence for Hypothesis \ref{hyp:online-vs-network}, that using an online search
engine was more commonplace than asking a friend.

@@

The second model predicts whether a respondent sought information about COVID-19
vaccinations by asking a person like friend, neighbor, or family member that
they know. Only three coefficients in this model were significant and help us
draw any conclusions on who is most likely to activate their personal social
network for informational support. In this study, I find that receiving
information about the vaccine from a doctor, their personal network, or a social
networking site is associated with seeking out more information. Those who
received information from a doctor or other medical professional were 3.08 times
more likely to seek information from a person such as a friend (\emph{p}
\textless{} 0.001). Moreover, it seems that receiving information from your
personal social network, such as a friend or relative, is associated with
seeking information from those same people; in fact, I find that those who did
are 3.32 more likely to do so (\emph{p} \textless{} 0.001). Finally, the
respondents who received information about the vaccine on a social networking
site were 55\% more likely to seek information from their personal network than
those who had not (\emph{p} \textless{} 0.01). The unexpected result of this
model is that very few factors predict personal social network activation, and
this model has the lowest McFadden's R\^{}2, indicating possible omitted
variables.

@@

\hypertarget{vaccination-views}{%
\subsection{Choosing to be Vaccinated}\label{vaccination-views}}

@@

Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. I find that receiving information from a
doctor or other medical profession is associated with 2.85 odds of choosing to
receive a COVID-19 vaccination (\emph{p} \textless{} 0.001) and that seeking
information from a doctor also increases the odds of vaccination by 4 (\emph{p}
\textless{} 0.001). I find that my respondents who received information on a
social networking site like Facebook or Twitter about the vaccines were 55\%
\textbf{less likely} to choose to get vaccinated than those who received no
information through that modality (\emph{p} \textless{} 0.001). However, I did
find that those who reached out to family or friends with their concerns were
77\% more likely to become vaccinated (\emph{p} \textless{} 0.05). Furthermore,
my respondents who held an Associate's degree or above had 3.6 higher odds of
becoming immunized (\emph{p} \textless{} 0.001). And finally, I found further
ethnoracial differences in my sample. I found that Hispanic-Latinos had 2.83
higher odds of vaccination than non-Hispanics (\emph{p} \textless{} 0.05) and
that my Asian sample had 4.73 higher odds as well over non-Asians (\emph{p}  =
0.09). See Figure \ref{fig:plot-model-3} for a visual representation of how
these different coefficients are related to vaccination outlook.

@@

\hypertarget{discussion}{%
\section{Discussion and Conclusion}\label{discussion}}

>>>>

\hypertarget{paper-2}{\chapter{Information seeking Behaviors for Information on COVID-19 Vaccinations}\label{paper-2}}

\hypertarget{abstract}{\section{Abstract}\label{abstract}}

@@

\hypertarget{intro-1}{\section{Introduction}\label{intro-1}}

@@

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
\citep{starbird19, kata10}. While no belief in false information can be thought
of as harmless \citep{douglas21} some discredited theories such as 'vaccines
cause autism' have major ramifications for both the individual and public
health. For example, a newfound public resistance to vaccination against Measles
by so-called 'anti-vaxxers' caused a 17\% increase in rates worldwide in 2019.
This increase killed  142,000 people, most of whom were children under the age
of five \citep{givetash19}. However, even in the ever-evolving research agenda
of misinformation and infodemiology \citep{eysenbach02}, much of the research
focuses on the 'push' or 'supply' side of information, like spaces where
individuals first encounter conspiracy theories or other information
\citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.

The lack of research in which modalities are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and well-being
of individuals in our society. Even outside of the misinformation literature,
much of the research conducted in social networks and communication focus on
senders, influencers, and persuasion strategies
\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955,
lazarsfeldPeopleChoice1944}, rather than on ``the receiver as an active
information seeker and processor''
\citep[][p. 344]{johnsonComprehensiveModelCancerRelated1993} \citep[for an exception,
see][]{eysenbach09}.

I use the case of information around COVID-19 vaccinations to explore the
variation of usage of information search modalities. In doing so, I seek to
answer how computer-mediated or interpersonal information seeking strategies
vary across populations as people search for information about COVID-19
vaccinations, and I investigate how these strategies affect vaccination uptake.
Specifically, this article answers two research questions: (1) How do
computer-mediated or interpersonal information seeking strategies vary across
populations? (2) How does the information search modality utilized affect
COVID-19 Vaccination uptake?

Before addressing the results to these research questions, I offer an overview
of the current state of social science literature in regards to information
seeking strategies and provide a description of the research methodology and
analytic sample. I then discuss the implications of these findings for the
sociological understanding of information search and vaccination uptake.

@@

One way to find information is to activate network ties to secure information
through a form of social support. Social support, while previously used
interchangeably with the terms social networks and social integration
\citep{houseStructuresProcessesSocial1988}, are the emotional, informational,
and instrumental assistance functions performed between social ties and have
strong and measurable association with health outcomes
\citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
Informational support is the process of seeking ``help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support'' \citep[][p. 640]{winemiller_etal93}.
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that ``facilitates
coping with life stresses… that may be exchanged among members of a support
network'' \citet[][p. 260]{brashersInformationSeekingAvoiding2002}. These
definitions help to differentiate between seeking information through social
ties or through something anonymous like online search; a need for coping or
deeper understanding of important matters is thought to sway that decision.

Social support has long been theorized to stem from core discussion networks and
much of the historical social support surveys only examined these core networks.
The underlying assumption is that individuals reach out to a handful of strong
ties when in need of support, which could be elicited in surveys using name
generators \citep{marsdenCoreDiscussionNetworks1987}. This approach has yielded
important insights, but largely overlooks crucial processes of resource
activation \citep{hurlbertCoreNetworksTie2000, perrySocialNetworkActivation2015,
smithDonPutMy2005}. For instance, \citet{smallSomeoneTalk2017} shows that
the core discussion network does not capture how people activate social support
in practice and indicates that people draw on much broader social connections
for support, reminiscent of the weak ties research by \citet{granovetterStrengthWeakTies1973}.
There is ongoing research investigating
how weak-tie support holds for different support types based on the architecture
put forward by \citet{houseStructuresProcessesSocial1988} of instrumental,
emotional, and informational support.

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of ``Googling'', or the utilization of internet search engines. As the
online environment began penetrating all facets of modern human life, it makes
sense that performing online search has become one of the most convenient
modalities for information search. \citet{smallSomeoneTalk2017} showed
that graduate students often confided in ``miscellaneous classmates encountered
down the hall'' (p. 176) instead of established and trusted confidants because
they simply were there at the right time.
% Ron: Is it that simple? I think you have a lot in common with ``misc classmates down the hall'' in comparison with, let's say, a random sample of same-aged Tucsonans.
I theorize that online search engines
may be the most frictionless and costless mode of support. No social capital or
relationship is necessary when choosing to utilize a search engine.

@@

There are important factors that can influence information seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}. UGT
posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s
\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible
with Lazarsfeld and Katz’s theory of two-step flow
\citep{katzPersonalInfluencePart1955} because people can choose their media and
the opinion leaders they follow. Modern-day theorists have extended UGT theory
and classified the uses and gratifications of the internet and of social media.
\citet{staffordDeterminingUsesGratifications2004} theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties.
\citet{leungGenerationalDifferencesContent2013} theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

@@

\begin{hyp}[H\ref{hyp:drgooglefriend}] \label{hyp:drgooglefriend}
Seeking information from experts, search engines, and other people
will be the most common modes of information search in comparison
to online forums and social networking sites. 
\end{hyp}

@@

The data used for this research project are based on original survey data
collected between December 03, 2021 through December 12, 2021. This survey was
hosted on Qualtrics and participants were paid and recruited using Amazon Turk
(MTurk). Potential MTurkers were invited to participate if they were located in
the United States, had a task rate approval of over 95 percent, had completed 50
tasks, and had not completed this survey in previous sessions. The total valid
survey responses (\emph{n} = 948) were selected from a total of 1,066
respondents; some responses were disqualified due to a few factors such as
detected usage of a VPN, random answer clicking (determined by illogical
responses), poor quality typed responses (e.g.\, social network alters
consistently named random nouns), or taking the survey more than once. The
sample is slightly gender unbalanced, skewing towards male respondents. For the
respondents who provided their zip code (p = 0.98), the sample is quite balanced
with a slight skew towards MTurkers in the South (p = 0.41).

The survey took an average of 24.48 minutes with a standard deviation of 13.23
minutes. The shortest valid survey took 3.75 minutes and the longest took 111.08
minutes. Participants received \$6.00 in compensation for their participation in
the survey \footnote{All funding for this survey was provided by a Grant from
the Summer Institute in Computational Social Science and the Russell Sage
Foundation.}. The survey consisted of two main parts. The first portion of the
survey is a replication of they survey conducted by
\citet{smallSomeoneTalk2017}. In this section, I expand Small's research on
support activation by segregating weak-tie social support into instrumental,
emotional, and informational categories
\citep[see][]{houseStructuresProcessesSocial1988}. The second part of the survey
focuses on network resource activation and information seeking behaviors of
individuals regarding COVID-19 vaccinations for this paper.

\input{tables/paper2/table-1-dep}

\hypertarget{measures}{\subsection{Measures}\label{measures}}

\hypertarget{sought-information}{\subsubsection{Sought Information}\label{sought-information}}

@@

Further dependent variables segment the above question into multiple options;
``How did you look for information about the COVID-19 vaccine?'' Respondents
were posed with 5 responses and `other,' of which they could select multiple.
The largest proportion, 44\%, asked their `doctor or another health
professional'. About 42\% said they asked, `a person like friend, neighbor, or
family member that [they] know'. An additional 41\% searched `for [their]
question using an online search engine such as Google or Bing'. About a quarter
of the sample, 27\%, `posted queries in an online discussion group, listserv, or
other online forum like a Facebook Group or Subreddit'. And finally, 18\% of the
sample `posted queries on a social networking site such as Facebook timeline,
Twitter status update, or LinkedIn'. Much of the question wording and the
specific categories of search were inspired by ICPSR project 37220
\citep{scanlon19}. While each survey is not a direct comparison to the other, \citet{scanlon19}'s 
research focused on patient activation and health care utilization 
and therefore provided relevant, already validated survey questions for this survey.

@@

Another dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received or plans to receive a vaccination
against COVID-19. For this survey, the number of doses or timeline of receipt
were less relevant to the research question. This variable instead focuses on
intent or opinion about the vaccine. About 87\% have a positive view about the
vaccine. This construct is made through the combination of two survey items. The
first item is actual vaccination status, obtained through the question `Did you
receive a COVID-19 vaccine?' 84\% of the sample said that they had indeed
received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}). As the
national vaccination rate is closer to 75\% \citep{cdc20}, this indicates some
bias in our sample that must be acknowledged: either MTurkers are more likely to
be vaccinated than the normal population (sampling bias) or there is some
conformity bias in the responses causing survey takers to provide false answers.
The second survey item that contributes to `Vaccination Outlook' was only given
to those who had not responded `yes' to their vaccination status. These
respondents were asked `Do you plan to receive a vaccine for the prevention of
the COVID-19 virus?' Of those who were asked this question (n = 147), 9\% said
they were `definitely yes' getting the vaccine; 9\% said they were `probably
yes' going to receive vaccine. The rest of the sample was more unsure: 15\% said
they `Might or might not,' 26\% said `Probably not,' and finally 41\% said they
would `definitely not' receive the vaccine. The variable `Vaccination Outlook'
indicates that either the respondent received a COVID-19 vaccine or either
probably or definitely will in the future.

\input{tables/paper2/table-2-ind}

\hypertarget{independent-variables}{\subsubsection{Independent Variables}\label{independent-variables}}

The first independent variables used in this analysis are based on the question,
`In the past 12 months, without searching for it, did you receive information
about the COVID-19 vaccine from \ldots{} (check all sources you received
information from).' This differs from the `How did you look for information'
question above because this is based on passive reception of information. The
largest proportion of respondents had received information from ``a person like
friend, neighbor, or family member that [they] know'' (\(\widehat{p}\) = 67\%).
Respondents also commonly received information from a television news channel or
a newspaper, about 65\% of the sample. 47\% of the sample had received
information from their doctor or other health professional, while 40\% received
information from a social networking site such as Facebook timeline, Twitter
status update, or LinkedIn. Finally, the lowest proportion of the sample had
received information from an online discussion group, listserv, or other online
forum like a Facebook group or subreddit (\(\widehat{p}\) = 35\%).

@@

\hypertarget{analysis}{\section{Analysis}\label{analysis}}

My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-ind} \&
\ref{tab:table-2-dep}, I present descriptive statistics for all study variables,
including variable ranges, means, and standard deviations. For this paper, I
rely heavily on logistic regression, modeled in \texttt{r}; specifically, I fit
a series of binomial generalized linear models with a logit link
\citep{venables2002a}, otherwise known as logistic regression model
\citep{hothorn2006handbook}. This approach is appropriate because the data are
non-nested, cross-sectional data with binary independent variables. In Table
\ref{tab:table-model-1}\footnote{All Tables in this paper were created with the
modelsummary package in \texttt{r} \citep{modelsummary}}, I fit a logistic
regression model predicting whether someone sought information about COVID-19
using their sources of information (`Received info') as well as various
demographic variables such as age, education level and race. Figure
\ref{fig:plot-model-1} then illustrates the relationship between the
coefficients and information seeking.\footnote{Figures in this paper were all
created using the \texttt{r} packages jtools \citep{jtools} and ggplot2
\citep{wickham_etal, wickham11}}. In Table \ref{tab:model-2-phi}, I disaggregate
information seeking behaviors by investigating the difference in proportions of
each of the 5 different avenues of seeking information about COVID-19: from
another person, from a doctor, on an online forum, on a social networking site,
or using an online search tool. I investigate these differences through a phi
coefficient \citep{warrens08}, otherwise known as a mean square contingency
coefficient, which is used to investigate the degree of association between two
binary variables.\footnote{To calculate the Phi Coefficient, I utilize the Psych
\texttt{r} package \citep{psych}} I then investigate the associations between my
predictors and the five information search modalities by modelling a series of
logistic regressions in Table \ref{tab:table-model-2}. Finally, in Table
\ref{tab:table-model-3}, I investigate whether there is a relationship between
information exposure sources, information seeking behaviors and the choice to
get vaccinated against COVID-19 through a logistic regression model predicting
Vaccination Outlook. Figure \ref{fig:plot-model-3} then illustrates the
relationship between the coefficients and vaccination outlook.

\hypertarget{results}{\section{Results}\label{results}}

\hypertarget{information seeking}{\subsection{Information Seeking}\label{information seeking}}

@@

\hypertarget{information-search-modalities}{\subsection{Information Search Modalities}\label{information-search-modalities}}

@@

To investigate how each information search modality is related to each other
using the Phi Coefficient ($\phi$) of binary association between each
Information Search modality pair. The Phi coefficient can be interpreted like a
correlation coefficient, with numbers closer to -1 indicating a very strong
negative relationship and those closer to positive 1 indicating a very strong
positive relationship (Warrens 2008). Table \ref{tab:model-2-phi} shows the
results of these coefficients. Out of the five information search modalities
investigated, there is evidence that the modalities are distinctly different
concepts because most coefficients fall under 0.3, the general cutoff for
correlation coefficients to indicate a relationship. There does seem to be a
relationship between Online Forums and social networking sites, possibly due to
an individual's latent propensity to use online networks over in-person
networks. These coefficients indicate a weak relationship between any two
modalities of information search and that respondents in my sample utilize each
of these a little bit differently.

I find that indeed the most common modalities are asking a doctor, asking a
friend, and asking a search engine which provides evidence to reject the null
hypothesis for Hypothesis
\ref{hyp:drgooglefriend}. However, because the modalities 95\% confidence
intervals in Table \ref{tab:table-1-ind} are overlapping, I fail to reject 
the null Hypothesis \ref{hyp:online-vs-network}, that using an online search
engine was more commonplace than asking a friend.

@@

The second model predicts whether a respondent sought information about COVID-19
vaccinations by asking a person like friend, neighbor, or family member that
they know. Only three coefficients in this model were significant and help us
draw any conclusions on who is most likely to activate their personal social
network for informational support. In this study, I find that receiving
information about the vaccine from a doctor, their personal network, or a social
networking site is associated with seeking out more information. Those who
received information from a doctor or other medical professional were 3.08 times
more likely to seek information from a person such as a friend (\emph{p}
\textless{} 0.001). Moreover, it seems that receiving information from your
personal social network, such as a friend or relative, is associated with
seeking information from those same people; in fact, I find that those who did
are 3.32 more likely to do so (\emph{p} \textless{} 0.001, see Table
\ref{tab:table-model-2}, ``Person'' model). Finally, the
respondents who received information about the vaccine on a social networking
site were 55\% more likely to seek information from their personal network than
those who had not (\emph{p} \textless{} 0.01). The unexpected result of this
model is that very few factors predict personal social network activation, and
this model has the lowest McFadden's R\^{2}, indicating possible omitted
variables.

@@

\hypertarget{vaccination-views}{\subsection{Choosing to be Vaccinated}\label{vaccination-views}}

@@

Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. I find that receiving information from a
doctor or other medical profession is associated with 2.85 odds of choosing to
receive a COVID-19 vaccination (\emph{p} \textless{} 0.001) and that seeking
information from a doctor also increases the odds of vaccination by 4 (\emph{p}
\textless{} 0.001). I find that my respondents who received information on a
social networking site like Facebook or Twitter about the vaccines were 55\%
\textbf{less likely} to choose to get vaccinated than those who received no
information through that modality (\emph{p} \textless{} 0.001). However, I did
find that those who reached out to family or friends with their concerns were
77\% more likely to become vaccinated (\emph{p} \textless{} 0.05). Furthermore,
my respondents who held an Associate's degree or above had 3.6 higher odds of
becoming immunized (\emph{p} \textless{} 0.001). And finally, I found further
ethnoracial differences in my sample. I found that Hispanic-Latinos had 2.83
higher odds of vaccination than non-Hispanics (\emph{p} \textless{} 0.05) and
that my Asian sample had 4.73 higher odds as well over non-Asians (\emph{p}  =
0.09). See Figure \ref{fig:plot-model-3} for a visual representation of how
these different coefficients are related to vaccination outlook. 'Gender, Other'
is likely an outlier with an inflated effect here due to only 6 participants
being coded as 'Other' for their gender.

@@

\hypertarget{discussion}{\section{Discussion and Conclusion}\label{discussion}}
